Predicting Tags for StackOverflow Posts

### 2013-03-16 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: 4c341b0b78582a9017bfb54ce784b28e477583f9 [formerly bbf712ad341b3b24cb674f265a3c4c95820a8053]
Former-commit-id: 0280f749441fc54204506a17727de8e6005809aa

A logistic regression technique was used in order to operationalize this fit measure.
For each post, three sets of tag groups were combined to most accurately sample tag activations while managing computer resource constraints:
The model's tag activations for the highest 200 tags, a weighted sample of 800 tags (weighted towards higher activation), and the tag activations for all tags that were chosen by the author of the post.
Each of these observations was assigned a category of 0 or 1 depending on if the tag was a chosen tag or not for that post (0 is not chosen).
Conceptually, if the model has good categorization power, the observations assigned 1 should have higher tag activations than the observations assigned 0.

@@

However using a single run of the \num{1000} posts was insufficient because there are two model components that require prior estimates of coefficients:
The offset measure to determine the top-five tags and associated activation and the sampling technique used to pick a representative set of tags for each post.
So model calibration was bootstrapped, where the coefficients from the previous run were used as estimates of coefficients for the next run.
The coefficients converged on best-fit values quickly (only required two sets of four iterations), and did not show any signs of instability.

@@

The final best-fit coefficients for each model component and formal statistical measurements are included in Tables \ref{tab:coeffs} and \ref{tab:fits} respectively.

@@

Note that all four coefficients for the run are strong predictors of tag use ($p<.01$), and model fit is satisfactory (McFadden's pseudo $R_{}^{2}=.46$, npv = .997, ppv = .70).
It is also interesting that although the attentional weighting ($W$) terms for the title and body were calibrated by the regression, they did not stray far from cognitively-plausible defaults
(see coefficients for title and body in Table \ref{tab:coeffs}).

@@

Note how the base level activation and contextual activation combine to predict tags that are both frequently used and contextually relevant.
For example, note that the \emph{javascript} tag leverages a combination of contextual activation and prior activation to achieve a high total activation.
Alternatively, the \emph{svg} tag relies almost entirely on context to achieve high activation.
And note that the model is by no means perfect.
For example, \emph{html} is not tagged by the author, but the model ranks it as the second highest tag.
And the author's tag \emph{firefox} is only ranked 8th by the model.

@@

\subsection{Classification Accuracy}

@@

\subsection{Potential Applications}

@@

\subsection{Comparison to \citeA{Kuo2011}}

@@

\subsection{Entropy and ACT-R's Attentional Weighting}

@@

\subsection{Current Model Issues}

Including the offset term in the model improved performance (see Figure \ref{fig:ROC}).
However by normalizing the top activations for all posts, the model cannot differentiate between a post where the top predicted tag is certain, and a post where the top-predicted tag is questionable.
One could argue that normalizing top activations for all posts should cause model performance to decrease, and the opposite was actually observed.
One hypothesis is that this normalization is required because the retrieval threshold of a tag is adjusted for each post, and changed so that only a small set of tags are retrieved for all posts.
Further research will explore this and other theories for the behavior of the offset component in the model.

\subsection{Future Planned Research}

Alongside exploring the offset component of the model, our main planned research is to include the post author's past tagging behavior as an additional model predictor.
We are exploring a Bayesian updating technique that would adjust prior tag activations from global priors to user's priors as more tagging information about the user is collected.
For the StackOverflow dataset, adding user's tagging history to the model should drastically improve predictive power for veteran users,
since tags are tied to programming languages and specific technologies, and programmers tend to specialize on a few set of tags that are of interest to them.
This technique could also be deployed, since a post author must be signed into StackOverflow before creating a new post.

>>>>

A logistic regression technique was used to operationalize this fit measure.
For each post, three sets of tag groups were combined to most accurately sample tag activations while managing computer resource constraints:
The top 20 tags having the highest model activation, a random sample of 400 tags, and the tags that were chosen by the author of the post.
Each of these observations was assigned a category of 0 or 1 depending on if the tag was a chosen tag or not for that post (0 is not chosen).
Conceptually, if the model has good categorization power, the observations assigned 1 should have higher tag activations than the observations assigned 0.

@@

However using a single run of the \num{1000} posts was insufficient because there are two model components that require prior estimates of coefficients:
The offset measure to determine the top-five tags and associated activation and the sampling technique used to pick the top 20 model-predicted tags for each post.
So model calibration was bootstrapped, where the coefficients from the previous run were used as estimates of coefficients for the next run.
The coefficients converged on best-fit values quickly (only required two sets of four iterations), and did not show any signs of instability.

@@

@@

The final best-fit coefficients for each model component and formal statistical measurements are included in Tables \ref{tab:coeffs} and \ref{tab:fits} respectively.
Note that all four coefficients for the run are strong predictors of tag use ($p<.01$), and model fit is satisfactory (McFadden's pseudo $R_{}^{2}=.46$, npv = .997, ppv = .70).
It is also interesting that although the attentional weighting ($W$) terms for the title and body were calibrated by the regression, they did not stray far from cognitively-plausible defaults
(see coefficients for title and body in Table \ref{tab:coeffs}).

@@

Note how the base level activation and contextual activation combine to predict tags that are both frequently used and contextually relevant.
For example, note that the \emph{javascript} tag leverages a combination of contextual activation and prior activation to achieve a high total activation.
Alternatively, the \emph{svg} tag relies almost entirely on context to achieve high activation.
And note that the model is by no means perfect.
For example, \emph{html} and \emph{jquery} are not tagged by the author, but the model ranks them as the second and third highest tag.
And the author's tag \emph{firefox} is only ranked 12th by the model.

@@

\subsubsection{Classification Accuracy}

@@

\subsubsection{Potential Applications}

@@

\subsubsection{Comparison to \citeA{Kuo2011}}

@@

\subsubsection{Entropy and ACT-R's Attentional Weighting}

@@

\subsubsection{Current Model Issues}

Including the offset term in the model improved performance (see Figure \ref{fig:ROC}).
However by normalizing the top activations for all posts, the model cannot differentiate between a post where the top predicted tag is certain, and a post where the top-predicted tag is questionable.
One could argue that normalizing top activations for all posts should cause model performance to decrease, and the opposite was actually observed.
One hypothesis is that this normalization is required because the retrieval threshold of a tag is adjusted for each post, and changed so that only a small set of tags are retrieved for all posts.
Further research will explore this and other theories for the behavior of the offset component.

\subsubsection{Future Planned Research}

Alongside exploring the offset component of the model, our main planned research is to include the post author's past tagging behavior as an additional model predictor.
We are exploring a Bayesian updating technique that would adjust prior tag activations from global priors to user's priors as more tagging information about the user is collected.
For the StackOverflow dataset, adding user's tagging history to the model should improve predictive power for veteran users,
since programmers tend to specialize on a few set of tags that are of interest to them.
This technique could also be deployed, since a post author must be signed in before creating a post.
